Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election 

### 2024-04-19 paper/paper(1).qmd
Add files via upload

**Age Adjustment**: In the census data, age is presented as a decimal number.
For consistency with the survey data, round this value to the nearest whole number.

**Gender Representation**: The gender classification in the census data, listed as either 'Male' or 'Female', aligns perfectly with the survey data, requiring no modifications.

**Provincial Data**: The listing of provinces in the census data, including "Newfoundland" and "Labrador", "Nova Scotia", "Quebec", "Saskatchewan", "Ontario", "Alberta", "British Columbia", "Prince Edward Island", "New Brunswick", and "Manitoba", matches that of the survey data, making no further adjustments necessary.

**Educational Levels**: The census data sorts educational attainment into eight categories, with one category for missing information.
Align these with the survey data's education classifications by grouping "Less than high school diploma or its equivalent" and missing data as "Limited Education"; "High school diploma or a high school equivalency certificate", "Trade certificate or diploma", "College, CEGEP, or other non-university certificate or diploma", "University certificate or diploma below the bachelor's level" as "Some Education"; and both "Bachelor's degree", and any university certification above a bachelor's degree as "Highly Educated".

**Religious Affiliation**: The "religion_has_affiliation" variable in the census data identifies if an individual has a religious affiliation, is uncertain, claims no religious affiliation, or if the response is missing.
For alignment with the survey data, consolidate into two groups: categorize as `YES` for those with a religious affiliation, uncertain, or missing responses (assuming missing responses indicate reluctance to disclose religious affiliation), and `NO` for those without any religious affiliation.

**Income Categories**: The Income_respondent field in the census dataset uses 7 income brackets to classify respondents' earnings.
To harmonize with the survey data's "income_before_tax" categories, reclassify these into three broader groups.
Designate incomes of "\$125,000 and more" to the "Upper Middle Class to Wealthy" group.
Categorize incomes of "\$50,000 to \$74,999", "\$75,000 to \$99,999", and "\$100,000 to \$124,999" as "Middle Class".
Assign "Less than \$25,000" and "\$25,000 to \$49,999" incomes to the "Lower Middle Class to Poor" group.

>>>>

**Age**: In the census data, age is presented as a decimal number.
For consistency with the survey data, round this value to the nearest whole number.

**Gender**: The gender classification in the census data, listed as either 'Male' or 'Female', aligns perfectly with the survey data, requiring no modifications.

**Province**: The listing of provinces in the census data, including "Newfoundland" and "Labrador", "Nova Scotia", "Quebec", "Saskatchewan", "Ontario", "Alberta", "British Columbia", "Prince Edward Island", "New Brunswick", and "Manitoba", matches that of the survey data, making no further adjustments necessary.

**Educational**: The census data sorts educational attainment into eight categories, with one category for missing information.
Align these with the survey data's education classifications by grouping "Less than high school diploma or its equivalent" and missing data as "Limited Education"; "High school diploma or a high school equivalency certificate", "Trade certificate or diploma", "College, CEGEP, or other non-university certificate or diploma", "University certificate or diploma below the bachelor's level" as "Some Education"; and both "Bachelor's degree", and any university certification above a bachelor's degree as "Highly Educated".

**Religious**: The "religion_has_affiliation" variable in the census data identifies if an individual has a religious affiliation, is uncertain, claims no religious affiliation, or if the response is missing.
For alignment with the survey data, consolidate into two groups: categorize as `YES` for those with a religious affiliation, uncertain, or missing responses (assuming missing responses indicate reluctance to disclose religious affiliation), and `NO` for those without any religious affiliation.

**Income**: The Income_respondent field in the census dataset uses 7 income brackets to classify respondents' earnings.
To harmonize with the survey data's "income_before_tax" categories, reclassify these into three broader groups.
Designate incomes of "\$125,000 and more" to the "Upper Middle Class to Wealthy" group.
Categorize incomes of "\$50,000 to \$74,999", "\$75,000 to \$99,999", and "\$100,000 to \$124,999" as "Middle Class".
Assign "Less than \$25,000" and "\$25,000 to \$49,999" incomes to the "Lower Middle Class to Poor" group.
